### 2015-01-19 src/introduction.Rnw
fix up intro

For this study, we experimented four classic mutation selection
techniques: Constrained \cite{wong1995reducing}, E-Selective
\cite{offutt1996anexperimental}, Javalanche \cite{javalanche} and
N-Selection \cite{offutt1993experimental}, along with two sampling
approaches: element based \cite{zhang2013ase} and operator based   sampling
\cite{wong1995reducing}. We compare test effectiveness of each of techniques
with pure random sampling. Our results show that in most cases there is no
statistically significant benefit for mutation selection techniques. Moreover,
in cases with statistically significant benefit, the gain is so low that is
essentially negligible.

@@

If we assume that testers would prefer adding test cases that increases the
mutation score, then a good strategy should reward the behavior of adding
non-redundant test cases and test suites with larger number of asserts.
Thus it should choose a set of mutants that are killed by a larger number
of such non-redundant tests at-least in comparison with random selection of
the same number of mutants as the chosen set. We could also ensure that a
reduction strategy does not miss out on important tests by running the set
of non-redundant tests against the full set of mutants to see how many of
the mutants were detected in comparison with the original number of detected
mutants. This can again be compared to the test cases selected by a random
sample of same number of mutants to see if the strategy performed better
at-least with respect to random sampling. Since this evaluation crtieria does
not depend on the mutation-adequacy of the test suite under consideration,
we can run the evaluation using real world projects which almost always have
non-adequate test suites.

>>>>

For this study, we experimented five classic mutation selection
techniques: Constrained \cite{wong1995reducing}, E-Selective
\cite{offutt1996anexperimental}, Javalanche \cite{javalanche},
Variable Reduction~\cite{namin2006finding} and N-Selection
\cite{offutt1993experimental}, along with two sampling approaches:
element based \cite{zhang2013ase} and operator based sampling
\cite{wong1995reducing}. We compare test effectiveness of each of techniques
with pure random sampling. Our results show that in most cases there is no
statistically significant benefit for mutation selection techniques. Moreover,
in cases with statistically significant benefit, the gain is so low that is
essentially negligible.

@@

If we assume that testers would prefer adding test cases that increases the
mutation score, then a good strategy should reward the behavior of adding
non-redundant test cases and test suites with larger number of asserts.
Thus it should choose a set of mutants that are killed by a larger number
of such non-redundant tests at-least in comparison with random selection
of the same number of mutants as the chosen set. We could also ensure that
a reduction strategy does not miss out on important tests by running the
set of non-redundant tests against the full set of mutants to see how many
of the mutants were detected in comparison with the original number of
detected mutants~\footnote{This is defined as the operator mutation score
by Mresa et al.~\cite{mresa1999efficiency}. But the term mutation score is
already a popular synonym for the mutation fraction detected. We call it the
strategy effectiveness in this paper}. This can again be compared to the test
cases selected by a random sample of same number of mutants to see if the
strategy performed better at-least with respect to random sampling. Since
this evaluation crtieria does not depend on the mutation-adequacy of the
test suite under consideration, we can run the evaluation using real world
projects which almost always have non-adequate test suites.
